The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-04 paper.tex
update

The main purpose of this study is to use three-dimensional\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{inclined} jet scenario is able to produce the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness (for eROSITA bubbles), and the spectra (for \textit{Fermi} bubbles).\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated gamma-ray spectra (colored lines in right column) of the Fermi bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      Simulated microwave spectra (colored lines in left) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.
  }
  \label{fig__gammaRay}
\end{figure*}

>>>>

The main purpose of this study is to use three-dimensional\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{inclined} jet scenario is able to produce\
the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness (for eROSITA bubbles), and the spectra (for \textit{Fermi} bubbles).\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__spectrum.png}
  \caption{
      Simulated microwave spectra (colored lines in left) averaged over $|l|<10^{\circ}$, $20^{\circ}<|b|<30^{\circ}$.\
      The data point represents the \textit{WMAP} data in the 23 GHz K band and the shaded area indicates the range\
      of synchrotron spectral indices allowed for the \textit{WMAP} haze \citep{Dobler_2008}.\
      Simulated gamma-ray spectra (colored lines in right column) of the Fermi bubbles calculated for a longitude range of\
      $|l|<10^{\circ}$ for different latitude bins.\
      The gray band represents the observational data of \citet{Ackermann2014}.\
      The rows from top to bottom show the microwave (left) and gamma-ray (left) spectra\
      with CRe spectra index $p=2.0, 2.2$ and $2.4$.
      %At larger $p$, the microwave spectrum was found to be steeper as $I_{\nu}\propto \nu^{-(p-1)/2}$.
  }
  \label{fig__gammaRay}
\end{figure*}
